OCMu64: a solver for One-sided Crossing Minimization

### 2024-09-20 tex/paper.tex
figures
reference figures

\section{Methods}
\subsection{Reductions}
\subparagraph{Fixed pairs}
To reduce the search space of all possible orderings of $B$, it is crucial to automatically
find as many fixed pairs in $B$ as possible. Ideally, one would be able to determine whether $u
\b v$ by inspecting only $u, v$. For example, the following result is well known \cite[Lemma
  1]{dujmovic_2004}, RR1 of \cite{dujmovic_2008}.

@@

We give a much stronger version of \cref{lem:weak}. In fact, \cref{lem:sfp} is the strongest
generalization possible when only considering $u, v$ themselves, without further inspection of
$A$ or the other elements of $B$ (see \cref{rem:strongest}). This also generalizes RR3 of
\cite{dujmovic_2008}.

@@

In practice, such a set $X$ can be found, if one exists, using a knapsack-like algorithm: for
each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a subset summing
to ${\leq{}(r(u, v), r(u, v))}$.

>>>>

\begin{figure}[t]
\centering
\hfill
\subfloat[An instance of \cref{lem:weak}.]{
\includegraphics[width=0.30\textwidth]{fig/simple.pdf}%
\label{fig:simple}
}
\hfill
\subfloat[Examples of blocking sets in blue.]{
\includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
\label{fig:blocking-set}
}
\hfill
\\
\subfloat[Examples of strongly fixed pairs.]{
\includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
\label{fig:strongly-fixed}
}
%% \subfloat[]{
%% \includegraphics[width=0.33\textwidth]{fig/gluing.pdf}%
%% \label{fig:gluing}
%% }
\caption{
  Various examples where $u\b v$, where $u,v\in B$ can freely move around and
  their neighbours in $A$ (on the dashed line) have fixed positions.}%
\label{fig}
\end{figure}

\section{Methods}
\subsection{Reductions}
\subparagraph{Fixed pairs}
To reduce the search space of all possible orderings of $B$, it is crucial to automatically
find as many fixed pairs in $B$ as possible. Ideally, one would be able to determine whether $u
\b v$ by inspecting only $u, v$. For example, the following result, shown in \cref{fig:simple} is well known \cite[Lemma
  1]{dujmovic_2004}, RR1 of \cite{dujmovic_2008}.

@@

We give a much stronger version of \cref{lem:weak}, with some examples in \cref{fig:strongly-fixed}. In fact, \cref{lem:sfp} is the strongest
generalization possible when only considering $u$ and $v$ themselves, without further inspection of
$A$ or the other elements of $B$ (see \cref{rem:strongest}). This also generalizes RR3 of
\cite{dujmovic_2008}.

@@

In practice, such a blocking set $X$ can be found, if one exists, using a knapsack-like algorithm: for
each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a subset summing
to ${\leq{}(r(u, v), r(u, v))}$. \cref{fig:blocking} shows some examples.
